---
title: "CODEBOOK"
author: "Tanakorn Dhamalongkrot"
date: "December 28, 2016"
output: html_document
---

##This is a code book

###The result from **run_analysis.R** is intended to answer five questions below
***
You should create one R script called run_analysis.R that does the following.  
1.Merges the training and the test sets to create one data set.  
2.Extracts only the measurements on the mean and standard deviation for each measurement.  
3.Uses descriptive activity names to name the activities in the data set  
4.Appropriately labels the data set with descriptive variable names.  
5.From the data set in step 4, creates a second, independent tidy data set with the average of each variable for each activity and each subject.  

#### As a result **run_analysis.R** will create the following result

Name             |   Type   |         Description  
-----------------|----------|-------------------------
allbind5         |data.table| Result from first four question  
allbind5tidy     |data.table| Result from fifth question  
allbind5.csv     | csv file | Conversion of allbind5  
allbind5tidy.csv | csv file | Conversion of allbind5tidy  
allbind5tidy.txt | txt file | Conversion of allbind5tidy  

###For **allbind5**  variable detail are listed as follows
**- vfeaturenumber**  
The mean and sd measurement for each of factor for using in this analysis. Displayed as variable code.  
**- subject**  
group of 30 volunteers within an age bracket of 19-48 years  
**- activitynumber**  
list of six activities (1=WALKING, 2=WALKING_UPSTAIRS, 3=WALKING_DOWNSTAIRS, 4=SITTING, 5=STANDING, 6=LAYING)  
**- activityname & activity**  
Activity name; WALKING, WALKING_UPSTAIRS, WALKING_DOWNSTAIRS, SITTING, STANDING, and LAYING  
**- value**  
Single value of each sample. The value is corespond to featurename.  
**- featurenumber**  
Same as vfeaturenumber. Except that there is no v as a code for mapping  
**- featurename**  
detailed featurename.  
**- Domain**  
Time and frequency notation  
**- Instrument**  
Type of sensor signal  
**- Variable**  
Classify between mean and sd  
**- Jerk**  
jerk signal and magnitude of three dimensional signal  
**- Magnitude**  
Magnitude of three dimensional signal  
**- Axis**  
Classify -x, -y, -z, the 3-axial signals  
**- Count**  
Number count of each variable in calculating average  
**- Average**  
Average value based on each variable.  

Step is listed as follows  

##1.Merges the training and the test sets to create one data set.  
First download the file and set command to execute winrar on the zip file  

Then read file subject, activity, X variables and combine the table

##2.Extracts only the measurements on the mean and standard deviation for each measurement.  
Classify feature that contain only mean() and std(). Set it as feature2

Select column to be used; subject, activity number, and "selected" feature
Then Read activity label and add activity label to allbind3 through the use of merge function
That is; allbind3 will be "selected" feature plus suject, activity number, and ,activity label

Then, reshape data by taking x variable and spread out in vfeaturenumber column. Leave the rest of data; subject, activitynumber, and activityname the same

##3.Uses descriptive activity names to name the activities in the data set  
Add featurename and featurenumber to allbind4 and add activity and feature column


##4.Appropriately labels the data set with descriptive variable names  
Classify whether it is time variable or frequency variable  
Time variable will be displayed for value of 1 while Freq will be displayed for value of 2  
Classify between Type of sensor signal  
Classify component of sensor acceleration signal, which are gravitational and body motion components  
Note that, if the information factor has NA, label will be start at NA  
Classify between mean and sd  
From unique(allbind5$feature), there is jerk signal and magnitude of three dimensional signal  
Classify -x, -y, -z, the 3-axial signals  
Finally, Make sure that all feature are counted. Note that there are 66 unique feature in this dataset.

##5.From the data set in step 4, creates a second, independent tidy data set with the average of each variable for each activity and each subject.
Create a data set with the average of each variable for each activity and each subject.  
Cal average separated by 30 subjects,6 Activity, and different 666 factors
allbind5tidy<-allbind5[,list(count=.N,average=mean(value)),by =key(allbind5)]

##Create tidy file
write.csv(allbind5,file="allbind5.csv")
write.csv(allbind5tidy,file="allbind5tidy.csv")
write.table(allbind5tidy,file="allbind5tidy.txt",row.names=FALSE)

##Make codebook.
library(rmarkdown)
render("CODEBOOK.Rmd",output_format="md_document")
render("CODEBOOK.Rmd")

##Make markdown
render("README.Rmd",output_format="md_document")
render("README.Rmd")


## Information from **allbind5** data.table
```{r}
library("memisc")
codebook(allbind5)
str(allbind5)
summary(allbind5)
```

## Information from **allbind5tidy** data.table
```{r}
codebook(allbind5tidy)
str(allbind5tidy)
summary(allbind5tidy)
```