---
title: "CODEBOOK"
author: "Tanakorn Dhamalongkrot"
date: "December 28, 2016"
output: html_document
---

##This is a code book

###The result from **run_analysis.R** is intended to answer five questions below
***
You should create one R script called run_analysis.R that does the following.  
1.Merges the training and the test sets to create one data set.  
2.Extracts only the measurements on the mean and standard deviation for each measurement.  
3.Uses descriptive activity names to name the activities in the data set  
4.Appropriately labels the data set with descriptive variable names.  
5.From the data set in step 4, creates a second, independent tidy data set with the average of each variable for each activity and each subject.  

#### As a result **run_analysis.R** will create the following result

Name             |   Type   |         Description  
-----------------|----------|-------------------------
allbind5         |data.table| Result from first four question  
allbind5tidy     |data.table| Result from fifth question  
allbind5.csv     | csv file | Conversion of allbind5  
allbind5tidy.csv | csv file | Conversion of allbind5tidy  
allbind5tidy.txt | txt file | Conversion of allbind5tidy  

###For **allbind5**  variable detail are listed as follows
**- vfeaturenumber**  
The mean and sd measurement for each of factor for using in this analysis. Displayed as variable code.  
**- subject**  
group of 30 volunteers within an age bracket of 19-48 years  
**- activitynumber**  
list of six activities (1=WALKING, 2=WALKING_UPSTAIRS, 3=WALKING_DOWNSTAIRS, 4=SITTING, 5=STANDING, 6=LAYING)  
**- activityname & activity**  
Activity name; WALKING, WALKING_UPSTAIRS, WALKING_DOWNSTAIRS, SITTING, STANDING, and LAYING  
**- value**  
Single value of each sample. The value is corespond to featurename.  
**- featurenumber**  
Same as vfeaturenumber. Except that there is no v as a code for mapping  
**- featurename**  
detailed featurename.  
**- Domain**  
Time and frequency notation  
**- Instrument**  
Type of sensor signal  
**- Variable**  
Classify between mean and sd  
**- Jerk**  
jerk signal and magnitude of three dimensional signal  
**- Magnitude**  
Magnitude of three dimensional signal  
**- Axis**  
Classify -x, -y, -z, the 3-axial signals  
**- Count**  
Number count of each variable in calculating average  
**- Average**  
Average value based on each variable.  

## Information from **allbind5** data.table
```{r}
library("memisc")
codebook(allbind5)
str(allbind5)
summary(allbind5)
```

## Information from **allbind5tidy** data.table
```{r}
codebook(allbind5tidy)
str(allbind5tidy)
summary(allbind5tidy)
```